---
title: "iStay"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{iStay}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global-options, include=FALSE}
if (requireNamespace("knitr", quietly = TRUE)) {
  kc <- get("opts_chunk", envir = asNamespace("knitr"))
  kc$set(
    collapse   = TRUE,
    comment    = "#>",
    fig.retina = 2,
    fig.align  = "center",
    fig.width  = 6,
    fig.height = 3,
    warning    = FALSE,
    message    = FALSE
  )
} else {
  warning("Package 'knitr' not available; vignette chunk options not set.")
}
options(width = 200, digits = 3)

paste0 <- base::paste0
paste  <- base::paste

```


```{r setup}
library(iStay)
```

<font color=#FF6600>
</font>

`iStay` (information-based measures of stability and related synchrony) is an R package that features a class of measures of community/ecosystem stability and related synchrony; the corresponding diversity-stability relationships are also assessed if biodiversity data are available. The information-based measures of stability are developed based on the Hill-number parameterized by an order q > 0; see Chao et al. (2025) for the relevant theory and methodological background. All measures are illustrated using biomass temporal data from the Jena experiment (Wagg et al. 2022).

Specifically, iStay features the following measures separately for three cases:

(1)	For a <u>single community</u>, it computes stability measures of order q > 0 and provides the stability profile which depicts the stability with respect to order q. When biodiversity data are available, the diversity-stability relationship is also assessed.

(2)	For <u>multiple communities</u>, it computes four measures (gamma, alpha and beta stability and synchrony) and provides the corresponding profiles. When biodiversity data are available, the diversity-stability and diversity-synchrony relationships are also assessed. 

(3)	For <u>hierarchies</u>, it computes three measures (gamma, alpha, and normalized beta stability at each hierarchical level) of order q > 0 and provides the stability profile which depicts the stability with respect to order q.


## How to cite

If you publish work based on results obtained using the iStay package, please cite both the associated methodology paper and the R package.


## Software needed to run iStay in R
- Required: [R](https://cran.r-project.org/)
- Suggested: [RStudio IDE](https://posit.co/products/open-source/rstudio/#Desktop)


## How to run iStay:

The `iStay` package can be downloaded from CRAN or Github [iStay_github](https://github.com/AnneChao/iStay) using the following commands. For a first-time installation, an additional visualization extension package (`ggplot2`) must be installed and loaded.

```{r, eval = FALSE}
## install iStay package from CRAN
# install.packages("iStay")  

## install the latest version from github
install.packages('devtools')
library(devtools)
install_github("AnneChao/iStay")

## import packages
library(iStay)
```


This package provides five main functions, listed below with their default arguments. Please refer to the package manual for detailed descriptions of each argument. 

- **Stay_Single**: computes the stability of time-series data (e.g., biomass, productivity) for a single assemblage.

```{r, eval=FALSE}
Stay_Single(data, order.q = c(1, 2), Alltime = TRUE, start_T = NULL, end_T = NULL)
```

- **Stay_Multiple**: computes gamma, alpha, and beta stability, as well as synchrony, for time-series data (e.g., biomass, productivity) across multiple assemblages.

```{r, eval=FALSE}
Stay_Multiple(data, order.q = c(1, 2), Alltime = TRUE, start_T = NULL, end_T = NULL)
```

- **Stay_Hier**: computes gamma, alpha, and normalized beta stability for time-series data (e.g., biomass, productivity) within hierarchical structures.

```{r, eval=FALSE}
Stay_Hier(data, mat, order.q = c(1, 2), Alltime = TRUE, start_T = NULL, end_T = NULL)
```

- **ggStay_qprofile**: graphs the q-profile of stability (and synchrony if is multiple assemblages) based on the output obtained from the function `Stay_Single`, `Stay_Multiple` or `Stay_Hier`.

```{r, eval=FALSE}
ggStay_qprofile(output)
```

- **ggStay_analysis**: plots the relationships between stability (and synchrony if is multiple assemblages) and an additional diversity (or other) variable based on the output obtained from the function `Stay_Single` or `Stay_Multiple`.

```{r, eval=FALSE}
ggStay_analysis(output, x_variable, by_group = NULL, model = "LMM")
```


## Data input format

For <u>Single community</u> analysis: the input data consist of a time series of biomass (or other relevant variables). It can also consist of multiple time series data of biomass (or other pertinent variables) that will calculate stability within each time series; biodiversity information is optional. 

For <u>Multiple communities</u> analysis: the input data consist of multiple time series data of biomass (or other relevant variables). Alternatively, users can provide a list of data frames, each containing multiple biomass time series; , where stability is calculated within each data frame; biodiversity information is optional. 

For <u>Hierarchies</u> analysis: the input data consist of multiple time series data of biomass (or other relevant variables), together with a structure matrix corresponding to the biomass data.

#### Time series of Biomass data

The biomass data in German Jena experiment are used here to demonstrate the use of the five functions; see Roscher (2004) and Weisser (2017) for more comprehensive description of the experimental design and the data details. We use the biomass time series collected from 76 plots in four blocks (B1, B2, B3, and B4) for illustrating all measures and depicting the corresponding diversity-stability relationships. In each block, plots were sown in a diversity gradient of 1, 2, 4, 8, or 16 plant species. Each diversity of plant species corresponds to three or four plots in the block. In each plot, the total biomass of all species was recorded annually from 2003 to 2024. And also recorded the biomass of each species each year from 2003 to 2024 except 2004. 

There are four datasets provided with the package: (1) 22-years biomass of plots data (`Jena_plot_biomass_data`), (2) 21-years biomass of species in each plot data (`Jena_species_biomass_data`), (3) hierarchical biomass data (`Jena_hierarchical_biomass_data`), (4) and hierarchical structure matrix data (`Jena_hierarchical_mat`). 


The first dataset (`Jena_plot_biomass_data`) is a list including 20 time series biomass dataframes by considering all possible block-sowndiv combinations (4 blocks and 5 levels of sown diversity). Each dataframe includes the plots (as rows) corresponding to same block and number of sown plants, and 22-years total biomass of all species (as columns) in each plot. 

This dataset is primarily intended for multiple-community analysis. For single-community analysis, the 20 data frames can be combined. The following example shows how to view the first ten rows and the first five columns of `Jena_plot_biomass_data` for single-community analysis, and the first five columns of the first data frame (B1_1) for multiple-community analysis.

```{r, eval=F}
data("Jena_plot_biomass_data")
single_plot <- do.call(rbind, Jena_plot_biomass_data)
head(round(single_plot[,1:5],2), 10)
```

```{r, echo=F}
data("Jena_plot_biomass_data")
single_plot <- do.call(rbind, Jena_plot_biomass_data)
head(round(single_plot[,1:5],2), 10)
```

```{r, eval=F}
data("Jena_plot_biomass_data")
multiple_plot <- Jena_plot_biomass_data
head(round(multiple_plot[[1]][,1:5],2), 10)
```

```{r, echo=F}
data("Jena_plot_biomass_data")
multiple_plot <- Jena_plot_biomass_data
head(round(multiple_plot[[1]][,1:5],2), 10)
```


The first dataset contains the total biomass of all species in each plot.  
The second dataset (`Jena_species_biomass_data`) contains species-level biomass for each plot. It is a list of 76 biomass time-series data frames, corresponding to all plots. Each data frame includes the species (as rows) in a given plot and 21 years of biomass (as columns). 

This dataset is primarily intended for multiple-community analysis. For single-community analysis, the 76 data frames can be combined. To illustrate, run the following code on `Jena_species_biomass_data` to view the first ten rows and the first five columns (columns 1 to 5) for single-community analysis. You can also view the first five columns (columns 1 to 5) of the first data frame (`B1A01_B1_16`) for multiple-community analysis.

```{r, eval=F}
data("Jena_species_biomass_data")
single_species <- do.call(rbind, Jena_species_biomass_data)
head(round(single_species[,1:5],2), 10)
```

```{r, echo=F}
data("Jena_species_biomass_data")
single_species <- do.call(rbind, Jena_species_biomass_data)
head(round(single_species[,1:5],2), 10)
```

```{r, eval=F}
data("Jena_species_biomass_data")
multiple_species <- Jena_species_biomass_data
head(round(multiple_species[[1]][,1:5],2), 10)
```

```{r, echo=F}
data("Jena_species_biomass_data")
multiple_species <- Jena_species_biomass_data
head(round(multiple_species[[1]][,1:5],2), 10)
```


For hierarchical analysis, we also use the species-level biomass data from each plot to construct a hierarchical structure with four levels: overall area, block, plot, and species. The third dataset (`Jena_hierarchical_biomass_data`) contains biomass data for hierarchical analysis, including all species in each plot (as columns) and 21 years of biomass (as rows). Note that year 2004 is omitted because species-level biomass was not recorded in that year. 

To illustrate, run the following code to view the first ten rows and the first five columns (columns 1 to 5): 

```{r, eval=F}
data("Jena_hierarchical_biomass_data")
head(round(Jena_hierarchical_biomass_data[,1:5],2), 10)
```

```{r, echo=F}
data("Jena_hierarchical_biomass_data")
head(round(Jena_hierarchical_biomass_data[,1:5],2), 10)
```


#### Structure matrix for hierarchies

For the `Jena_hierarchical_biomass_data` dataset, the corresponding structure matrix is provided in `Jena_hierarchical_mat`. 

This matrix contains three columns representing the hierarchical levels from highest to lowest (excluding the overall area): "Block", "Plot", and "Species". Each row in `Jena_hierarchical_mat` corresponds to a row in the biomass dataset and specifies the category to which that biomass measurement belongs at each hierarchical level. 

To illustrate, run the following code to view the first ten rows: 

```{r, eval=F}
data("Jena_hierarchical_mat")
head(Jena_hierarchical_mat, 10)
```

```{r, echo=F}
data("Jena_hierarchical_mat")
head(Jena_hierarchical_mat, 10)
```


## Computing plot stability in a single plot with plotting plot stability-profile and relationship between plot stability and diversity variable. 

Based on biomass data, `Stay_Single()` computes the stability of each community (plot) for a specified order q.  
The function `ggStay_qprofile()` is used to plot the stability profile.  
If diversity information is combined with the output of `Stay_Single()`, the function `ggStay_analysis()` can be used to plot the relationship between stability and diversity.  

For the stability profile, the following example sets order q from 0.1 to 2.0 in increments of 0.1, using 22 years of biomass data from only two plots ("B1A04" and "B4A14") to avoid an overly complicated graph.  
For the diversity–stability relationship, the example uses the default setting of order q (q = 1 and q = 2) and the 22-year biomass data from all 76 plots.  

To illustrate, run the following code to view the first ten rows of the output:

```{r, eval=F}
single_plot <- do.call(rbind, Jena_plot_biomass_data)
output_single_q <- Stay_Single(data = single_plot[which(rownames(single_plot) %in% c("B1_4.B1A04", "B4_2.B4A14")),],
                               order.q = seq(0.1,2,0.1),
                               Alltime=TRUE)
head(output_single_q, 10)
```

```{r, echo=F}
single_plot <- do.call(rbind, Jena_plot_biomass_data)
output_single_q <- Stay_Single(data = single_plot[which(rownames(single_plot) %in% c("B1_4.B1A04", "B4_2.B4A14")),],
                               order.q=seq(0.1,2,0.1), 
                               Alltime = TRUE)
head(output_single_q, 10)
```

The output above includes the plot or community name (`Plot/Community`), the order q (`Order_q`), and the corresponding stability value (`Stability`).  

To obtain the stability profile, run the following code:

```{r, fig.align='center'}
ggStay_qprofile(output = output_single_q)
```

To obtain the diversity–stability relationship plot, first combine the diversity information with the output of `Stay_Single()`.  
The following code demonstrates this process and shows only the first ten rows of the result:

```{r, eval=FALSE}
output_single_div <- Stay_Single(data = single_plot, order.q = c(1,2), Alltime = TRUE)
output_single_div <- data.frame(output_single_div,
                                log2_sowndiv = log2(as.numeric(do.call(rbind,
                                                   strsplit(output_single_div[,1],"[._]+"))[,2])),
                                block=do.call(rbind, strsplit(output_single_div[,1],"[._]+"))[,1])
colnames(output_single_div)[1] <- c("Plot/Community")
head(output_single_div, 10)
```

```{r, echo=FALSE}
output_single_div <- Stay_Single(data=single_plot, order.q=c(1,2), Alltime=TRUE)
output_single_div <- data.frame(output_single_div,
                                log2_sowndiv=log2(as.numeric(do.call(rbind,
                                                   strsplit(output_single_div[,1],"[._]+"))[,2])),
                                block=do.call(rbind, strsplit(output_single_div[,1],"[._]+"))[,1])
colnames(output_single_div)[1] <- c("Plot/Community")
head(output_single_div, 10)
```

```{r,fig.width = 7}
ggStay_analysis(output = output_single_div, x_variable = "log2_sowndiv", 
                by_group = "block", model = "LMM")
```


## Computing plot stability in multiple plots with plotting plot stability-profile and relationship between plot stability and diversity variable. 

Based on biomass data, `Stay_Multiple()` computes the stability of each group of multiple communities (plots) for a specified order q.  
The function `ggStay_qprofile()` is used to plot the stability profile.  
If diversity information is combined with the output of `Stay_Multiple()`, the function `ggStay_analysis()` can be used to plot the relationship between stability and diversity.  

For the stability profile, the following example sets order q from 0.1 to 2.0 in increments of 0.1, using 22 years of biomass data from only two groups of multiple communities ("B1_1" and "B3_2") to avoid an overly complicated graph.  
For the diversity–stability relationship, the example uses the default setting of order q (q = 1 and q = 2) and the 22-year biomass data from all 20 groups of multiple communities.  

To illustrate, run the following code to view the first ten rows of the output:

```{r, eval=F}
multiple_plot <- Jena_plot_biomass_data
output_multi_q <- Stay_Multiple(data = multiple_plot[which(names(multiple_plot) %in% c("B1_1",  "B3_2"))],
                                order.q = seq(0.1,2,0.1), Alltime=TRUE)
head(output_multi_q, 10)
```

```{r, echo=F}
multiple_plot <- Jena_plot_biomass_data
output_multi_q <- Stay_Multiple(data=multiple_plot[which(names(multiple_plot) %in% c("B1_1",  "B3_2"))],
                                    order.q=seq(0.1,2,0.1), Alltime=TRUE)
rownames(output_multi_q) <- NULL
head(output_multi_q, 10)
```

The output above includes the group name (`Site`), the order q (`Order_q`), and the corresponding stability and synchrony measures (`Gamma`, `Alpha`, `Beta` stability, and `Synchrony`).  

To obtain the stability and synchrony profiles, run the following code:

```{r, fig.align='center', fig.width = 7, fig.height = 4.5}
ggStay_qprofile(output=output_multi_q)
```

To obtain the diversity–stability relationship plot, first combine the diversity information with the output of `Stay_Multiple()`.  
The following code demonstrates this process and displays only the first ten rows of the result: 

```{r, eval=FALSE}
output_multi_div <- Stay_Multiple(data=multiple_plot, order.q=c(1,2), Alltime=TRUE)

output_multi_div <- data.frame(output_multi_div,
                               log2_sowndiv = log2(as.numeric(do.call(rbind, strsplit(output_multi_div[, 1], "_"))[, 2])),
         block = do.call(rbind, strsplit(output_multi_div[, 1], "_"))[, 1])
rownames(output_multi_div) <- NULL
head(cbind(output_multi_div[,1:2], round(output_multi_div[3:6],3), output_multi_div[,7:8]), 10)
```

```{r, echo=FALSE}
output_multi_div <- Stay_Multiple(data = multiple_plot, order.q = c(1,2), Alltime = TRUE)

output_multi_div <- data.frame(output_multi_div,
                               log2_sowndiv = log2(as.numeric(do.call(rbind, strsplit(output_multi_div[, 1], "_"))[, 2])),
         block = do.call(rbind, strsplit(output_multi_div[, 1], "_"))[, 1])
rownames(output_multi_div) <- NULL
head(cbind(output_multi_div[,1:2], round(output_multi_div[3:6], 3), output_multi_div[,7:8]), 10)
```

```{r,fig.width = 8, fig.height=9.5}
ggStay_analysis(output = output_multi_div, x_variable = "log2_sowndiv", 
                    by_group = "block", model = "LMM")
```


The examples above use the total biomass of all species in each plot (`Jena_plot_biomass_data`) to calculate plot-level stability.  
The following example uses the biomass of individual species in each plot (`Jena_species_biomass_data`) to calculate species-level stability. 


## Computing species stability in a single species in each plot with plotting species stability-profile and relationship between species stability and diversity variable. 

Based on biomass data, `Stay_Single()` computes the stability of each species in each plot for a specified order q.  
The function `ggStay_qprofile()` is used to plot the stability profile.  
If diversity information is combined with the output of `Stay_Single()`, the function `ggStay_analysis()` can be used to plot the relationship between stability and diversity.  

For the stability profile, the following example sets order q from 0.1 to 2.0 in increments of 0.1, using 21 years of biomass data from only two species in plot B1A06 ("Ant.odo" and "Cam.pat") to avoid an overly complicated graph.  
For the diversity–stability relationship, the example uses the default setting of order q (q = 1 and q = 2) and the 21-year biomass data of all 462 species (each species in each plot). 

To illustrate, run the following code to display the first ten rows of the output:

```{r, eval=F}
single_species <- do.call(rbind, Jena_species_biomass_data)
output_single_species_q <- Stay_Single(data = single_species[which(rownames(single_species) %in% c("B1A06_B1_16.BM_Ant.odo", "B1A06_B1_16.BM_Cam.pat")),],
                                       order.q=seq(0.1,2,0.1), Alltime=TRUE)
head(output_single_species_q, 10)
```

```{r, echo=F}
single_species <- do.call(rbind, Jena_species_biomass_data)
output_single_species_q <- Stay_Single(data = single_species[which(rownames(single_species) %in% c("B1A06_B1_16.BM_Ant.odo", "B1A06_B1_16.BM_Cam.pat")),],
                                       order.q=seq(0.1,2,0.1), Alltime=TRUE)
head(output_single_species_q, 10)
```

The output above includes the plot or community name (`Plot/Community`), the order q (`Order_q`), and the corresponding stability value (`Stability`).  

To obtain the stability profile, run the following code:

```{r, fig.align='center'}
ggStay_qprofile(output = output_single_species_q)
```

To obtain the diversity–stability relationship plot, first combine the diversity information with the output of `Stay_Single()`.  
The following code demonstrates this process and displays only the first ten rows of the result: 

```{r, eval=FALSE}
output_single_species_div <- Stay_Single(data = single_species,
                                         order.q = c(1,2), Alltime=TRUE)
output_single_species_div <- data.frame(output_single_species_div,
                              log2_sowndiv = log2(as.numeric(do.call(rbind,
                                      strsplit(output_single_species_div[,1],"[._]+"))[,3])),
                              block = do.call(rbind,
                                    strsplit(output_single_species_div[,1],"[._]+"))[,2])
head(output_single_species_div, 10)
```

```{r, echo=FALSE}
output_single_species_div <- Stay_Single(data=single_species,
                                         order.q=c(1,2), Alltime=TRUE)
output_single_species_div <- data.frame(output_single_species_div,
                             log2_sowndiv=log2(as.numeric(do.call(rbind,
                                      strsplit(output_single_species_div[,1],"[._]+"))[,3])),
                              block=do.call(rbind,
                                    strsplit(output_single_species_div[,1],"[._]+"))[,2])
head(output_single_species_div, 10)
```

```{r,fig.width = 7}
ggStay_analysis(output=output_single_species_div, x_variable="log2_sowndiv",
                    by_group="block", model="LMM")
```


## Computing species stability in multiple species with plotting species stability-profile and relationship between species stability and diversity variable. 

Based on biomass data, `Stay_Multiple()` computes the species-level stability of multiple species within each plot for a specified order q.  
The function `ggStay_qprofile()` is used to plot the stability profile.  
If diversity information is combined with the output of `Stay_Multiple()`, the function `ggStay_analysis()` can be used to plot the relationship between stability and diversity.  

For the stability profile, the following example sets order q from 0.1 to 2.0 in increments of 0.1, using 21 years of biomass data from only two plots with multiple species ("B1A04_B1_4" and "B4A14_B4_2") to avoid an overly complicated graph.  
For the diversity–stability relationship, the example uses the default setting of order q (q = 1 and q = 2) and the 21-year biomass data from all 76 groups (plots) of multiple species.  

To illustrate, run the following code to display the first ten rows of the output:


```{r, eval=F}
multiple_species <- Jena_species_biomass_data
output_multi_species_q <- Stay_Multiple(data = multiple_species[which(names(multiple_species) %in% c("B1A04_B1_4", "B4A14_B4_2"))],
                                            order.q = seq(0.1,2,0.1), Alltime = TRUE)
head(output_multi_species_q, 10)
```

```{r, echo=F}
multiple_species <- Jena_species_biomass_data
output_multi_species_q <- Stay_Multiple(data=multiple_species[which(names(multiple_species) %in% c("B1A04_B1_4", "B4A14_B4_2"))],
                                            order.q=seq(0.1,2,0.1), Alltime=TRUE)
rownames(output_multi_species_q) <- NULL
head(output_multi_species_q, 10)
```

The output above includes the group name (`Site`), the order q (`Order_q`), and the corresponding stability and synchrony measures (`Gamma`, `Alpha`, `Beta` stability, and `Synchrony`).  

To obtain the stability and synchrony profiles, run the following code:

```{r, fig.align='center', fig.width = 7, fig.height = 4.5}
ggStay_qprofile(output = output_multi_species_q)
```

To obtain the diversity–stability relationship plot, first combine the diversity information with the output of `Stay_Multiple()`.  
The following code demonstrates this process and displays only the first ten rows of the result: 

```{r, eval=FALSE}
output_multi_species_div <- Stay_Multiple(data = multiple_species,
                                          order.q = c(1,2), Alltime = TRUE)
output_multi_species_div <- data.frame(output_multi_species_div,
                             log2_sowndiv = log2(as.numeric(do.call(rbind,
                                      strsplit(output_multi_species_div[,1],"[._]+"))[,3])),
                             block = do.call(rbind,
                                   strsplit(output_multi_species_div[,1],"_"))[,2])
head(output_multi_species_div, 10)
```

```{r, echo=FALSE}
output_multi_species_div <- Stay_Multiple(data = multiple_species,
                                          order.q = c(1,2), Alltime = TRUE)
output_multi_species_div <- data.frame(output_multi_species_div,
                             log2_sowndiv = log2(as.numeric(do.call(rbind,
                                      strsplit(output_multi_species_div[,1],"[._]+"))[,3])),
                             block = do.call(rbind,
                                   strsplit(output_multi_species_div[,1],"_"))[,2])
rownames(output_multi_species_div) <- NULL
head(output_multi_species_div, 10)
```

```{r,fig.width = 8, fig.height=9.5}
ggStay_analysis(output=output_multi_species_div, x_variable="log2_sowndiv",
                    by_group="block", model="LMM")
```



## Computing stability of hierarchical strucuture with plotting stability-profile. 

Based on biomass data and the corresponding structure matrix, `Stay_Hier()` computes the stability of each hierarchical level for a specified order q.  
The function `ggStay_qprofile()` is used to plot the stability profile.  

In the following example, order q is set from 0.1 to 2.0 in increments of 0.1, using 21 years of biomass data.  

To illustrate, run the following code to display the first ten rows of the output:

```{r, eval=F}
data("Jena_hierarchical_biomass_data")
data("Jena_hierarchical_mat")
output_hier_q <- Stay_Hier(data=Jena_hierarchical_biomass_data, mat=Jena_hierarchical_mat,
                           order.q=seq(0.1,2,0.1), Alltime=TRUE)
head(output_hier_q, 10)
```

```{r, echo=F}

data("Jena_hierarchical_biomass_data")
data("Jena_hierarchical_mat")
output_hier_q <- Stay_Hier(data=Jena_hierarchical_biomass_data, mat=Jena_hierarchical_mat,
                           order.q=seq(0.1,2,0.1), Alltime=TRUE)
head(cbind(output_hier_q[,1:2], round(output_hier_q[,3:6],3)), 10)
```

The output above includes the hierarchical level (`Hier`), the order q (`Order_q`), and the corresponding stability measures for each level (`Gamma`, `Alpha`, `Beta` stability, and `Synchrony`).  

To obtain the gamma and alpha stability profiles at each hierarchical level, as well as the decomposition of the overall stability profile and the synchrony profile across hierarchical levels, run the following code: 

```{r, fig.align='left', fig.width = 5, fig.height = 3}
hierplot <- ggStay_qprofile(output=output_hier_q)
hierplot[[1]]
```

```{r, fig.align='left', fig.width = 9.5, fig.height = 3}
hierplot[[2]]
```


## References

Anne Chao, Robert K. Colwell, Johnny Shia. (2025)
A continuum of information-based temporal stability measures and their decomposition across hierarchical level.
doi:https://doi.org/10.1101/2025.08.20.671203

Roscher C. Schumacher, J., Baade, J. et al. (2004)
The role of biodiversity for element cycling and trophic interactions: an experimental approach in a grassland community Basic and Applied Ecology, 5, 107-121. https://doi.org/10.1078/1439-1791-00216

Weisser, W. W., Roscher, C., Meyer, S. T., et al. (2017) Biodiversity effects on ecosystem functioning in a 15-year grassland experiment: Patterns, mechanisms, and open questions. Basic and Applied Ecology, 23, 1-73. https://doi.org/10.1016/j.baae.2017.06.002

Wagg, C., Roscher, C., Weigelt, A. et al. (2022) Biodiversity–stability relationships strengthen over time in a long-term grassland experiment. Nature Communications 13, 7752. https://doi.org/10.1038/s41467-022-35189-2


